Detecting threats of violence in YouTube comments

### 2016-02-18 submission.tex
Minor changes
Updated Random forest results in baseline system table

      & MaxEnt & SVM & Random Forest \\
      \midrule
      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $0.3582$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
      Bag of lemmas & $0.5902$ & $0.5982$ & $0.3483$ \\
      Bigrams & $0.4856$ & $0.4887$ & $\textbf{0.4683}$ \\
      Trigrams & $0.2776$ & $0.2856$ & $0.2673$ \\

>>>>

      & MaxEnt & SVM & Random Forest \\
      \midrule
      Bag of word forms & $\textbf{0.6123}$ & $\textbf{0.6068}$ & $\textbf{0.5918}$ \\ % SVM bag of words er bare best dersom word form + uPOS ikke er med i tabellen
      Bag of lemmas & $0.5902$ & $0.5982$ & $0.5856$ \\
      Bigrams & $0.4856$ & $0.4887$ & $0.4944$ \\
      Trigrams & $0.2776$ & $0.2856$ & $0.2859$ \\
